### 2010-02-03 doc/manuals/configuration/configuration_manual.tex
Started adding information about sechandlers

\subsection{Security Handlers}\label{sec:Security Handlers}
\subsubsection{Identity Mapping}\label{sec:identitymap-shc}
\subsubsection{ARC Authorization}\label{sec:arcautz-shc}
\subsubsection{Delegation Collector}\label{sec:delegcollector-shc}
\subsubsection{Delegation Handler}\label{sec:deleghandler-shc}
\subsubsection{Username Token}\label{sec:unametoken-shc}
\subsubsection{Username Token}\label{sec:x509token-shc}
%\subsubsection{SAML Token}% samltoken.handler
%\subsubsection{SAML Single Sign-On}% saml2ssoassertionconsumer.handler

>>>>

\subsection{Security Handlers}\label{sec:Security Handlers}
Security Handlers are components which extract security related properties of
the message, collect then and use for making authorization decisions.

The Security Handlers are assigned MCCs and are arranged in queues. Each queue
is processing specific messages. Usually MCCs implement two queues named 
"incoming" and "outgoing" for the messages going through chain to service
and returning back respectively.

The Security Handlers in each queue are applied sequentially and if any
produces negative result processing stops are error is raised.

The Security Handlers are added to MCCs through \texttt{SecHandler} configuration
element put inside \texttt{Component} or \texttt{Service} elements. The
\texttt{name} attribute specifies which plugin to be used. And queue is 
specified by \texttt{event} attribute. Each configured instance can be 
optionally assigned identifier through \texttt{id} attribute. Tne content
of \texttt{SecHandler} is specific for every kind of plugin.
Example is below:
\begin{lstlisting}[language=xml]
...
<Component name="mcc1.service" id="mcc1">
  <next id="mcc2"/>
  <SecHandler name="handler1" event="incoming" id="id1">
  </SecHandler>
</Component>
...
\end{lstlisting}

\subsubsection{ARC Authorization}\label{sec:arcautz-shc}
This Security Handler applies set of Policy Decision Point (PDP) element to the
message and then produces decision result using combining algorithm specified in 
\texttt{action} attribute of \texttt{SecHandler} element. For desciption of PDP
elements see section \ref{sec:Policy Decision Points}.

Available combining algorithms are:
\begin{description}
\item[breakOnDeny] - processing stops when PDP returns Deny decision. The SecHandler
produces negative result. This is a default algorith.
\item[breakOnAllow] - processing stopr when PDP return Allow decision. The SecHandler
produces positive result.
\item[breakAlways] - processing stops after first PDP. Produced result is used as
result of SecHandler.
\item[breakNever] - all PDPs are applied. Result of last PDP is used as result of 
SecHandler.
\end{description}

\subsubsection{Identity Mapping}\label{sec:identitymap-shc}

\subsubsection{Delegation Collector}\label{sec:delegcollector-shc}
\subsubsection{Delegation Handler}\label{sec:deleghandler-shc}
\subsubsection{Username Token}\label{sec:unametoken-shc}
\subsubsection{Username Token}\label{sec:x509token-shc}
%\subsubsection{SAML Token}% samltoken.handler
%\subsubsection{SAML Single Sign-On}% saml2ssoassertionconsumer.handler
